\documentclass[11pt]{article}
\usepackage[vmargin=1.0in, hmargin=1.0in]{geometry}
\usepackage{setspace}
\begin{document}
This document contains a listing of the different commands that are exposed
through LibExpertSystem. This is a continually evolving document so it always
helps to view the source code to LibExpertSystem. 

The original use of LibExpertSystem was for implementing wavefront scheduling
as an expert system that interfaced with LLVM. This was my masters thesis and
the code was written specifically with the thesis in mind. After finishing my
thesis it was necessary to rewrite significant portions of the wavefront
scheduling code as well as LibExpertSystem to make it more useful and robust. 

This document currently has two sections: the LLVM IO router and new functions.


\section*{LLVM IO Router}
During my thesis I had to choose between debugging output and getting a valid
resultant program. This was because LLVM and CLIPS use standard out for
different purposes. In LLVM, standard out is used to write bitcode to a file.
In CLIPS, standard out is used to print things out to the console. This meant
using console redirect operators would cause both resultant program code and
any debugging messages to be saved to the redirected file. 

In a recent version of LibExpertSystem, I added the LLVM I/O router that is
responsible for printing to llvm::errs() which is where debug information
should be sent to for printing instead of standard out. CLIPS provides a
logical router system to make it super easy to write to different kinds of
files, streams, etc. This router system was used to add a new router titled
"llvm" which will write any data given to llvm::errs(). While this is a nice
feature it does mean that the llvm io router has to be mentioned explicitly if
one wants to use it. Thus, I modified the llvm print function to \emph{capture}
all output and not pass it to standard out at all. This means that all commands
that print to an IO router will be piped to llvm::errs(). 

\section*{New Commands}
\end{document}
